自动微分以及它在物理模拟中的应用\fivestar

### 2021-04-29 paper/paper.tex
tikzimage

\begin{figure}
    \centerline{\includegraphics[width=0.88\columnwidth,trim={0 0cm 0 0cm},clip]{tradeoff2.pdf}}
    \caption{(a) Treeverse算法~\cite{Griewank1992}示意图，其中$\eta(\tau, \delta) \equiv \left(\begin{matrix} \tau + \delta \\ \delta \end{matrix}\right)=\frac{(\tau+\delta)!}{\tau!\delta!}$。(b) Bennett算法对应$k=3$的示意图~\cite{Bennett1973,Levine1990}，其中$P$和$Q$分别代表了计算和反计算。}\label{fig:tradeoff}
\end{figure}

>>>>

\begin{figure}
    \centerline{\includegraphics[width=0.88\columnwidth,trim={0 0cm 0 0cm},clip]{tradeoff2.pdf}}
    \caption{(a) Treeverse算法~\cite{Griewank1992}示意图，其中$\eta(\tau, \delta) \equiv \left(\begin{matrix} \tau + \delta \\ \delta \end{matrix}\right)=\frac{(\tau+\delta)!}{\tau!\delta!}$。(b) Bennett算法对应$k=3$的示意图~\cite{Bennett1973,Levine1990}，其中$P$和$P^{-1}$分别代表了计算和反计算。}\label{fig:tradeoff}
\end{figure}
